Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-30 paper.tex
add number of augmentations, augmentation-matrix image

\newcommand{\numAugraphyAugmentations}{\emph{n}}

@@

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

\section{Introduction}
The modern world provides a plethora of tasks that require the need for automated and intelligent solutions for handling unstructured data.
Often, this data is in the form of documents, and these documents may appear noisy, especially if they have been captured from the physical world via printing, scanning, or photocopying processes.
Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human annotations like highlighting or pencil marks can add noise to the page.

Many tasks involving machine learning are impacted by document noise.
High-level tasks like document classification and information extraction must often be able to perform on noisily scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
Further, the lower-level task of document de-noising tackles the document noise problem more directly by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
Such tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries.}
    \scalebox{0.9}{
    \begin{tabular}{lccccc}
    \toprule
        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & & \xmark &  & \cmark & MIT \\ 
        \emph{Albumentations} \cite{ref_albumentations} &  & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & & \xmark & & \cmark & MIT \\
        \emph{Pytorch} \cite{pytorch} & & \xmark & \cmark & \cmark & BSD-style \\
        \emph{DocCreator} \cite{ref_DocCreator} & & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{figure}
\centering
\scalebox{0.33}{
\includegraphics[]{pipeline.png}}
\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
\end{figure}

@@

Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
These augmentations are listed in Table~\ref{tab:augmentations}.
As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.

@@

\begin{figure}
\includegraphics[width=\textwidth]{augmentations1.png}
\caption{Examples of each augmentation.} \label{fig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{augmentations2.png}
\caption{Examples of each augmentation.} \label{fig3}
\end{figure}

@@

\subsection{Model Architecture}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library.
This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.

This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step.
After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively.
The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is ``unpacking" higher-dimensional features from its low-dimensional latent representation.
After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier.
Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions.
This final convolution uses the sigmoid function as its activation function.
All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

@@

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{sidebyside.png}
\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
\end{figure}

>>>>

\newcommand{\numAugraphyAugmentations}{\emph{26}}

@@

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
We discuss the Augraphy tool, showing how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document de-noising, as well as generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

\section{Introduction}
Life in the modern world involves a plethora of tasks that require automated and intelligent solutions for handling unstructured data.
Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been altered in the physical world by printing, scanning, or photocopying processes.
Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.

Many machine learning operations involving documents are impacted by the presence of noise; high-level tasks like document classification and information extraction are often expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
Further, the lower-level task of document de-noising tackles the document noise problem more directly by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
Such tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

@@

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \scalebox{0.9}{
    \begin{tabular}{lccccc}
    \toprule
        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168& \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

@@

\begin{figure}
\centering
\scalebox{0.33}{
\includegraphics[]{figures/pipeline.png}}
\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
\end{figure}

@@

Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
These augmentations are listed in Table~\ref{tab:augmentations}, and examples are shown in Figure~\ref{fig:augraphy-examples-github}.
As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.

@@

%\begin{figure}
%\includegraphics[width=\textwidth]{augmentations1.png}
%\caption{Examples of each augmentation.} \label{fig2}
%\end{figure}
%
%\begin{figure}
%\includegraphics[width=\textwidth]{augmentations2.png}
%\caption{Examples of each augmentation.} \label{fig3}
%\end{figure}

\begin{figure}
    \centering\scalebox{0.34}{
    \includegraphics{figures/augraphy_examples_github.png}}
    \caption{A subset of various \emph{Augraphy} augmentations on sample images.}
    \label{fig:augraphy-examples-github}
\end{figure}

@@

\subsection{Model Architecture}
To evaluate Augraphy, we trained an off-the-shelf Nonlinear Activation-Free Network, \cite{NAFNet}.
This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.

@@

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{figures/sidebyside.png}
\caption{Validation images (left), with the images predicted by the NoisyOffice (center) and Augraphy (right) models.}
\end{figure}
